{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2018-05-01 sftrends_manu.tex
ECSS initial revision done

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\{Declarations of interest: none}
  \vspace{0.1in}
  \\ Version Date:   Thu Apr 19 17:53:28 2018 -0700
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% overall trends, years
%latex.default(tab[, -c(1, 2)], file = "", rowlabel = "Analyte/Station",     caption = cap.val, caption.loc = "top", rgroup = vars, n.rgroup = rep(nrow(tab)/3,         3), cgroup = c("Annual"), n.cgroup = c(2), rowname = stats,     label = "tab:trndsann")%
\begin{table}[!tbp]
\caption{Summaries of flow-normalized trends in nitrogen forms for all stations and annual aggregations. Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. *$p<0.05$\label{tab:trndsann}} 
\begin{center}
\begin{tabular}{lll}
\hline\hline
\multicolumn{1}{l}{\bfseries Analyte/Station}&\multicolumn{2}{c}{\bfseries Annual}\tabularnewline
\cline{2-3}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{1976-1995}&\multicolumn{1}{c}{1996-2013}\tabularnewline
\hline
{\bfseries DIN}&&\tabularnewline
~~C10&1.3 \footnotesize{(\textbf{0.8})*}&1.4 \footnotesize{(-3.1)*}\tabularnewline
~~C3&0.3 \footnotesize{(\textbf{2.2})*}&0.5 \footnotesize{(-0.1)*}\tabularnewline
~~D19&0.4 \footnotesize{(\textbf{0.2})*}&0.4 \footnotesize{(-1.9)*}\tabularnewline
~~D26&0.4 \footnotesize{(\textbf{0.4})*}&0.5 \footnotesize{(-1.2)*}\tabularnewline
~~D28&0.4 \footnotesize{(\textbf{0.1})*}&0.4 \footnotesize{(-3.1)*}\tabularnewline
~~D4&0.3 \footnotesize{(\textbf{0.6})*}&0.4 \footnotesize{(-0.3)*}\tabularnewline
~~D6&0.4 \footnotesize{(\textbf{1.8})*}&0.5 \footnotesize{(-0.3)*}\tabularnewline
~~D7&0.4 \footnotesize{(\textbf{1.7})*}&0.5 \footnotesize{(-0.7)*}\tabularnewline
~~MD10&0.4 \footnotesize{(-1.1)*}&0.3 \footnotesize{(-2.4)*}\tabularnewline
~~P8&1.3 \footnotesize{(\textbf{2.5})*}&1.7 \footnotesize{(-2)*}\tabularnewline
\hline
{\bfseries NH$_{4}^{+}$}&&\tabularnewline
~~C10&0.1 \footnotesize{(-3.4)*}&0 \footnotesize{(-5.2)*}\tabularnewline
~~C3&0.2 \footnotesize{(\textbf{3.7})*}&0.3 \footnotesize{(\textbf{0})}\tabularnewline
~~D19&0 \footnotesize{(\textbf{0.4})*}&0 \footnotesize{(-1.7)*}\tabularnewline
~~D26&0.1 \footnotesize{(\textbf{2.2})*}&0.1 \footnotesize{(-1.5)*}\tabularnewline
~~D28&0 \footnotesize{(-1.1)*}&0 \footnotesize{(-1.4)*}\tabularnewline
~~D4&0 \footnotesize{(\textbf{0.9})*}&0.1 \footnotesize{(\textbf{0})}\tabularnewline
~~D6&0.1 \footnotesize{(\textbf{2.4})*}&0.1 \footnotesize{(-0.5)*}\tabularnewline
~~D7&0.1 \footnotesize{(\textbf{1.5})*}&0.1 \footnotesize{(-1.2)*}\tabularnewline
~~MD10&0.1 \footnotesize{(-2.8)*}&0 \footnotesize{(-1.1)*}\tabularnewline
~~P8&0.2 \footnotesize{(\textbf{4.9})*}&0.1 \footnotesize{(-10.3)*}\tabularnewline
\hline
{\bfseries NO$_{2}^{-}$/NO$_{3}^{2-}$}&&\tabularnewline
~~C10&1.2 \footnotesize{(\textbf{1.4})*}&1.4 \footnotesize{(-3)*}\tabularnewline
~~C3&0.1 \footnotesize{(-0.1)*}&0.2 \footnotesize{(\textbf{0.7})*}\tabularnewline
~~D19&0.4 \footnotesize{(-0.1)*}&0.4 \footnotesize{(-1.9)*}\tabularnewline
~~D26&0.3 \footnotesize{(\textbf{0})}&0.4 \footnotesize{(-1.1)*}\tabularnewline
~~D28&0.4 \footnotesize{(-0.2)*}&0.4 \footnotesize{(-3.1)*}\tabularnewline
~~D4&0.3 \footnotesize{(\textbf{0.7})*}&0.3 \footnotesize{(-0.4)*}\tabularnewline
~~D6&0.3 \footnotesize{(\textbf{1.3})*}&0.4 \footnotesize{(-0.3)*}\tabularnewline
~~D7&0.4 \footnotesize{(\textbf{0.7})*}&0.4 \footnotesize{(-0.7)*}\tabularnewline
~~MD10&0.4 \footnotesize{(-1)*}&0.3 \footnotesize{(-2.5)*}\tabularnewline
~~P8&1.2 \footnotesize{(\textbf{1.7})*}&1.5 \footnotesize{(-0.6)*}\tabularnewline
\hline
\end{tabular}\end{center}
\end{table}

% trends in no23, nh at p8
%latex.default(totab, file = "", rowlabel = "Period", caption = cap.val,     caption.loc = "top", rgroup = segs, n.rgroup = c(2, rep(4,         2)), cgroup = vars, n.cgroup = c(2, 2), rowname = cats,     label = "tab:p8chg")%
\begin{table}[!tbp]
\caption{Summaries of flow-normalized trends in nitrite/nitrate and ammonium (mg L$^{-1}$) concentrations before and after \ac{wwtp} upgrades upstream of station P8. Upgrades were completed in 2006 at the City of Stockton \ac{wwtp} (San Joaquin County, \cref{fig:stock}). Summaries are  medians and percent change per year in parentheses (increasing in bold).  Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Increasing values are in bold-italics. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$\label{tab:p8chg}} 
\begin{center}
\begin{tabular}{lllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Period}&\multicolumn{2}{c}{\bfseries NO$_{2}^{-}$/NO$_{3}^{2-}$}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NH$_{4}^{+}$}\tabularnewline
\cline{2-3} \cline{5-6}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{\% change}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{\% change}\tabularnewline
\hline
{\bfseries Annual}&&&&&\tabularnewline
~~1976-2006&1.3&\textbf{2}*&&0.2&\textbf{2.8}*\tabularnewline
~~2007-2013&1.4&-1.9*&&0.1&-16.6*\tabularnewline
\hline
{\bfseries Seasonal, pre}&&&&&\tabularnewline
~~Spring&1.2&\textbf{1.6}*&&0.2&\textbf{1.4}*\tabularnewline
~~Summer&1&\textbf{2.4}*&&0.1&\textbf{3.3}*\tabularnewline
~~Fall&1.3&\textbf{2.2}*&&0.2&\textbf{4.9}*\tabularnewline
~~Winter&1.5&\textbf{2.1}*&&0.7&\textbf{4.8}*\tabularnewline
\hline
{\bfseries Seasonal, post}&&&&&\tabularnewline
~~Spring&1.3&-1.6*&&0.1&-16.2*\tabularnewline
~~Summer&0.9&-4.3*&&0.1&-15.7*\tabularnewline
~~Fall&1.5&-1.7*&&0.1&-19.3*\tabularnewline
~~Winter&2.2&-0.8*&&0.2&-26.7*\tabularnewline
\hline
\end{tabular}\end{center}
\end{table}

@@

~~D26&0.4 \footnotesize{(\textbf{0.7})*}&0.3 \footnotesize{(\textbf{0.4})*}&0.4 \footnotesize{(\textbf{1})*}&0.6 \footnotesize{(\textbf{0.3})}\tabularnewline

@@

~~C10&0.1 \footnotesize{(-2.3)*}&0 \footnotesize{(-6.8)*}&0.1 \footnotesize{(-7.1)*}&0.3 \footnotesize{(-1.5)*}\tabularnewline
~~C3&0.2 \footnotesize{(\textbf{3.9})*}&0.2 \footnotesize{(\textbf{4})*}&0.3 \footnotesize{(\textbf{3.8})*}&0.2 \footnotesize{(\textbf{2.9})*}\tabularnewline
~~D19&0.1 \footnotesize{(\textbf{0.4})*}&0 \footnotesize{(-1.7)*}&0 \footnotesize{(\textbf{1.2})*}&0.1 \footnotesize{(\textbf{2.5})*}\tabularnewline

@@

~~D28&0.1 \footnotesize{(-0.5)}&0 \footnotesize{(-3.7)*}&0 \footnotesize{(-1.6)*}&0.1 \footnotesize{(\textbf{1.7})*}\tabularnewline
~~D4&0.1 \footnotesize{(\textbf{1.7})*}&0 \footnotesize{(\textbf{1})*}&0 \footnotesize{(-0.7)}&0.1 \footnotesize{(\textbf{2})*}\tabularnewline

@@

~~D7&0.1 \footnotesize{(\textbf{3.3})*}&0 \footnotesize{(\textbf{2})*}&0.1 \footnotesize{(-2.8)*}&0.1 \footnotesize{(\textbf{1.7})*}\tabularnewline
~~MD10&0.1 \footnotesize{(-1.8)*}&0 \footnotesize{(-6.5)*}&0 \footnotesize{(-3.3)*}&0.2 \footnotesize{(\textbf{0.4})}\tabularnewline
~~P8&0.2 \footnotesize{(\textbf{3.9})*}&0.1 \footnotesize{(\textbf{1.8})*}&0.2 \footnotesize{(\textbf{7})*}&0.6 \footnotesize{(\textbf{7})*}\tabularnewline

@@

~~C3&0.2 \footnotesize{(\textbf{0.7})*}&0.1 \footnotesize{(-1)*}&0.1 \footnotesize{(-0.3)}&0.2 \footnotesize{(\textbf{1})*}\tabularnewline

@@

~~D28&0.5 \footnotesize{(\textbf{0.7})*}&0.2 \footnotesize{(-0.1)}&0.3 \footnotesize{(\textbf{0.2})}&0.7 \footnotesize{(-1)*}\tabularnewline

@@

~~D6&0.4 \footnotesize{(-0.2)}&0.3 \footnotesize{(\textbf{4.1})*}&0.3 \footnotesize{(\textbf{1.4})*}&0.4 \footnotesize{(-1)*}\tabularnewline
~~D7&0.4 \footnotesize{(-1)*}&0.3 \footnotesize{(\textbf{3.4})*}&0.4 \footnotesize{(\textbf{0.4})}&0.4 \footnotesize{(-3.6)*}\tabularnewline

@@

~~P8&1.2 \footnotesize{(\textbf{2})*}&0.9 \footnotesize{(\textbf{2.3})*}&1.1 \footnotesize{(\textbf{2})*}&1.4 \footnotesize{(\textbf{1})*}\tabularnewline

@@

~~C10&1.1 \footnotesize{(-4.1)*}&1.3 \footnotesize{(-3.1)*}&1.6 \footnotesize{(-2)*}&1.7 \footnotesize{(-3.4)*}\tabularnewline

@@

~~D19&0.5 \footnotesize{(-2.8)*}&0.2 \footnotesize{(-1)*}&0.3 \footnotesize{(-1.6)*}&0.7 \footnotesize{(-2.3)*}\tabularnewline
~~D26&0.5 \footnotesize{(-1.9)*}&0.3 \footnotesize{(-1.7)*}&0.4 \footnotesize{(-1)*}&0.6 \footnotesize{(-0.8)*}\tabularnewline
~~D28&0.5 \footnotesize{(-3)*}&0.2 \footnotesize{(-4.9)*}&0.2 \footnotesize{(-4.9)*}&0.7 \footnotesize{(-2.1)*}\tabularnewline
~~D4&0.4 \footnotesize{(\textbf{0})}&0.4 \footnotesize{(-1)*}&0.4 \footnotesize{(-0.9)*}&0.5 \footnotesize{(\textbf{0.6})*}\tabularnewline
~~D6&0.5 \footnotesize{(-0.2)*}&0.5 \footnotesize{(-1)*}&0.5 \footnotesize{(-0.3)*}&0.5 \footnotesize{(-0.1)}\tabularnewline

@@

~~MD10&0.4 \footnotesize{(-2.3)*}&0.2 \footnotesize{(-3.7)*}&0.2 \footnotesize{(-4.4)*}&1 \footnotesize{(-1.8)*}\tabularnewline

@@

~~C10&0 \footnotesize{(-4.2)*}&0 \footnotesize{(-6.1)*}&0 \footnotesize{(-8.5)*}&0.1 \footnotesize{(-7.3)*}\tabularnewline
~~C3&0.3 \footnotesize{(\textbf{1})*}&0.3 \footnotesize{(-0.8)*}&0.4 \footnotesize{(-0.5)*}&0.2 \footnotesize{(-0.1)}\tabularnewline
~~D19&0 \footnotesize{(-1.9)*}&0 \footnotesize{(-0.4)}&0 \footnotesize{(-2.2)*}&0.1 \footnotesize{(-1.8)*}\tabularnewline

@@

~~D28&0 \footnotesize{(-1.7)*}&0 \footnotesize{(-0.2)}&0 \footnotesize{(-2.4)*}&0.1 \footnotesize{(-3.1)*}\tabularnewline
~~D4&0.1 \footnotesize{(\textbf{0.3})}&0 \footnotesize{(-1.3)*}&0.1 \footnotesize{(-0.3)}&0.1 \footnotesize{(\textbf{1})*}\tabularnewline
~~D6&0.1 \footnotesize{(-0.7)*}&0.1 \footnotesize{(-1)*}&0.1 \footnotesize{(\textbf{0.3})}&0.1 \footnotesize{(-0.3)*}\tabularnewline
~~D7&0.1 \footnotesize{(-2.2)*}&0 \footnotesize{(-2.1)*}&0.1 \footnotesize{(\textbf{1.3})*}&0.1 \footnotesize{(-0.4)*}\tabularnewline
~~MD10&0 \footnotesize{(-1.4)*}&0 \footnotesize{(-0.1)}&0 \footnotesize{(-0.8)*}&0.1 \footnotesize{(-4.3)*}\tabularnewline

@@

~~D19&0.4 \footnotesize{(-2.9)*}&0.2 \footnotesize{(-1)*}&0.3 \footnotesize{(-1.5)*}&0.6 \footnotesize{(-2.2)*}\tabularnewline

@@

~~D28&0.5 \footnotesize{(-3)*}&0.2 \footnotesize{(-5.4)*}&0.2 \footnotesize{(-5.2)*}&0.7 \footnotesize{(-1.7)*}\tabularnewline
~~D4&0.3 \footnotesize{(-0.1)}&0.3 \footnotesize{(-1)*}&0.3 \footnotesize{(-1)*}&0.4 \footnotesize{(\textbf{0.4})*}\tabularnewline
~~D6&0.4 \footnotesize{(-0.1)}&0.4 \footnotesize{(-1)*}&0.4 \footnotesize{(-0.4)*}&0.4 \footnotesize{(-0.1)}\tabularnewline

@@

~~MD10&0.4 \footnotesize{(-2.6)*}&0.1 \footnotesize{(-4.5)*}&0.2 \footnotesize{(-5.4)*}&1 \footnotesize{(-1.4)*}\tabularnewline
~~P8&1.3 \footnotesize{(-1.1)*}&1.1 \footnotesize{(-3.1)*}&1.6 \footnotesize{(-0.3)*}&2.2 \footnotesize{(\textbf{0})}\tabularnewline

>>>>

\begin{singlespace}
\title{{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^{1*}$, Thomas W. Jabusch$^2$, Philip R. Trowbridge$^2$, David B. Senn$^2$}}
  \\\\{\textit {\normalsize $^*$Corresponding author: \href{mailto:marcusb@sccwrp.org}{marcusb@sccwrp.org}}}
  \\\\{\textit {\normalsize $^1$Southern California Coastal Water Research Project}}
  \\{\textit {\normalsize 3535 Harbor Blvd, Suite 110, Costa Mesa, CA 92626}}
  \\\\{\textit {\normalsize $^2$San Francisco Estuary Institute}}
	\\{\textit {\normalsize 4911 Central Ave, Richmond, CA 94804}}
  \vspace{1in}
  \\{Declarations of interest: none}
  \vspace{0.1in}
  \\ Version Date:   Fri Apr 20 16:59:41 2018 -0700
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% overall trends, years
%latex.default(tab[, -c(1, 2)], file = "", rowlabel = "Analyte/Station",     caption = cap.val, caption.loc = "top", rgroup = vars, n.rgroup = rep(nrow(tab)/3,         3), cgroup = c("Annual"), n.cgroup = c(2), rowname = stats,     label = "tab:trndsann")%
\begin{table}[!tbp]
\caption{Summaries of flow-normalized trends in nitrogen forms for all stations and annual aggregations. Summaries are  medians (mg L$^{-1}$) and percent change per year in parentheses (increasing in bold). Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. *$p<0.05$\label{tab:trndsann}} 
\begin{center}
\begin{tabular}{lll}
\hline\hline
\multicolumn{1}{l}{\bfseries Analyte/Station}&\multicolumn{2}{c}{\bfseries Annual}\tabularnewline
\cline{2-3}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{1976-1995}&\multicolumn{1}{c}{1996-2013}\tabularnewline
\hline
{\bfseries DIN}&&\tabularnewline
~~C10&1.3 \footnotesize{(\textbf{0.8})*}&1.4 \footnotesize{(-3.1)*}\tabularnewline
~~C3&0.3 \footnotesize{(\textbf{2.2})*}&0.5 \footnotesize{(-0.1)*}\tabularnewline
~~D19&0.4 \footnotesize{(\textbf{0.2})*}&0.4 \footnotesize{(-1.9)*}\tabularnewline
~~D26&0.4 \footnotesize{(\textbf{0.4})*}&0.5 \footnotesize{(-1.2)*}\tabularnewline
~~D28&0.4 \footnotesize{(\textbf{0.1})*}&0.4 \footnotesize{(-3.1)*}\tabularnewline
~~D4&0.3 \footnotesize{(\textbf{0.6})*}&0.4 \footnotesize{(-0.3)*}\tabularnewline
~~D6&0.4 \footnotesize{(\textbf{1.8})*}&0.5 \footnotesize{(-0.3)*}\tabularnewline
~~D7&0.4 \footnotesize{(\textbf{1.7})*}&0.5 \footnotesize{(-0.7)*}\tabularnewline
~~MD10&0.4 \footnotesize{(-1.1)*}&0.3 \footnotesize{(-2.4)*}\tabularnewline
~~P8&1.3 \footnotesize{(\textbf{2.5})*}&1.7 \footnotesize{(-2.0)*}\tabularnewline
\hline
{\bfseries NH$_{4}^{+}$}&&\tabularnewline
~~C10&0.1 \footnotesize{(-3.4)*}&0.0 \footnotesize{(-5.2)*}\tabularnewline
~~C3&0.2 \footnotesize{(\textbf{3.7})*}&0.3 \footnotesize{(\textbf{0.0})}\tabularnewline
~~D19&0.0 \footnotesize{(\textbf{0.4})*}&0.0 \footnotesize{(-1.7)*}\tabularnewline
~~D26&0.1 \footnotesize{(\textbf{2.2})*}&0.1 \footnotesize{(-1.5)*}\tabularnewline
~~D28&0.0 \footnotesize{(-1.1)*}&0.0 \footnotesize{(-1.4)*}\tabularnewline
~~D4&0.0 \footnotesize{(\textbf{0.9})*}&0.1 \footnotesize{(\textbf{0.0})}\tabularnewline
~~D6&0.1 \footnotesize{(\textbf{2.4})*}&0.1 \footnotesize{(-0.5)*}\tabularnewline
~~D7&0.1 \footnotesize{(\textbf{1.5})*}&0.1 \footnotesize{(-1.2)*}\tabularnewline
~~MD10&0.1 \footnotesize{(-2.8)*}&0.0 \footnotesize{(-1.1)*}\tabularnewline
~~P8&0.2 \footnotesize{(\textbf{4.9})*}&0.1 \footnotesize{(-10.3)*}\tabularnewline
\hline
{\bfseries NO$_{2}^{-}$/NO$_{3}^{2-}$}&&\tabularnewline
~~C10&1.2 \footnotesize{(\textbf{1.4})*}&1.4 \footnotesize{(-3.0)*}\tabularnewline
~~C3&0.1 \footnotesize{(-0.1)*}&0.2 \footnotesize{(\textbf{0.7})*}\tabularnewline
~~D19&0.4 \footnotesize{(-0.1)*}&0.4 \footnotesize{(-1.9)*}\tabularnewline
~~D26&0.3 \footnotesize{(\textbf{0.0})}&0.4 \footnotesize{(-1.1)*}\tabularnewline
~~D28&0.4 \footnotesize{(-0.2)*}&0.4 \footnotesize{(-3.1)*}\tabularnewline
~~D4&0.3 \footnotesize{(\textbf{0.7})*}&0.3 \footnotesize{(-0.4)*}\tabularnewline
~~D6&0.3 \footnotesize{(\textbf{1.3})*}&0.4 \footnotesize{(-0.3)*}\tabularnewline
~~D7&0.4 \footnotesize{(\textbf{0.7})*}&0.4 \footnotesize{(-0.7)*}\tabularnewline
~~MD10&0.4 \footnotesize{(-1.0)*}&0.3 \footnotesize{(-2.5)*}\tabularnewline
~~P8&1.2 \footnotesize{(\textbf{1.7})*}&1.5 \footnotesize{(-0.6)*}\tabularnewline
\hline
\end{tabular}\end{center}
\end{table}

% trends in no23, nh at p8
%latex.default(totab, file = "", rowlabel = "Period", caption = cap.val,     caption.loc = "top", rgroup = segs, n.rgroup = c(2, rep(4,         2)), cgroup = vars, n.cgroup = c(2, 2), rowname = cats,     label = "tab:p8chg")%
\begin{table}[!tbp]
\caption{Summaries of flow-normalized trends in nitrite/nitrate and ammonium (mg L$^{-1}$) concentrations before and after \ac{wwtp} upgrades upstream of station P8. Upgrades were completed in 2006 at the City of Stockton \ac{wwtp} (San Joaquin County, \cref{fig:stock}). Summaries are  medians and percent change per year in parentheses (increasing in bold).  Changes and significance estimates are based on seasonal Kendall tests of flow-normalized results within each time period. Increasing values are in bold-italics. Months for each season are Spring: MAM, Summer: JJA, Fall: SON, Winter: DJF. *$p<0.05$\label{tab:p8chg}} 
\begin{center}
\begin{tabular}{lllcll}
\hline\hline
\multicolumn{1}{l}{\bfseries Period}&\multicolumn{2}{c}{\bfseries NO$_{2}^{-}$/NO$_{3}^{2-}$}&\multicolumn{1}{c}{\bfseries }&\multicolumn{2}{c}{\bfseries NH$_{4}^{+}$}\tabularnewline
\cline{2-3} \cline{5-6}
\multicolumn{1}{l}{}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{\% change}&\multicolumn{1}{c}{}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{\% change}\tabularnewline
\hline
{\bfseries Annual}&&&&&\tabularnewline
~~1976-2006&1.3&(\textbf{2.0})*&&0.2&(\textbf{2.8})*\tabularnewline
~~2007-2013&1.4&(-1.9)*&&0.1&(-16.6)*\tabularnewline
\hline
{\bfseries Seasonal, pre}&&&&&\tabularnewline
~~Spring&1.2&(\textbf{1.6})*&&0.2&(\textbf{1.4})*\tabularnewline
~~Summer&1.0&(\textbf{2.4})*&&0.1&(\textbf{3.3})*\tabularnewline
~~Fall&1.3&(\textbf{2.2})*&&0.2&(\textbf{4.9})*\tabularnewline
~~Winter&1.5&(\textbf{2.1})*&&0.7&(\textbf{4.8})*\tabularnewline
\hline
{\bfseries Seasonal, post}&&&&&\tabularnewline
~~Spring&1.3&(-1.6)*&&0.1&(-16.2)*\tabularnewline
~~Summer&0.9&(-4.3)*&&0.1&(-15.7)*\tabularnewline
~~Fall&1.5&(-1.7)*&&0.1&(-19.3)*\tabularnewline
~~Winter&2.2&(-0.8)*&&0.2&(-26.7)*\tabularnewline
\hline
\end{tabular}\end{center}
\end{table}

@@

~~D26&0.4 \footnotesize{(\textbf{0.7})*}&0.3 \footnotesize{(\textbf{0.4})*}&0.4 \footnotesize{(\textbf{1.0})*}&0.6 \footnotesize{(\textbf{0.3})}\tabularnewline

@@

~~C10&0.1 \footnotesize{(-2.3)*}&0.0 \footnotesize{(-6.8)*}&0.1 \footnotesize{(-7.1)*}&0.3 \footnotesize{(-1.5)*}\tabularnewline
~~C3&0.2 \footnotesize{(\textbf{3.9})*}&0.2 \footnotesize{(\textbf{4.0})*}&0.3 \footnotesize{(\textbf{3.8})*}&0.2 \footnotesize{(\textbf{2.9})*}\tabularnewline
~~D19&0.1 \footnotesize{(\textbf{0.4})*}&0.0 \footnotesize{(-1.7)*}&0.0 \footnotesize{(\textbf{1.2})*}&0.1 \footnotesize{(\textbf{2.5})*}\tabularnewline

@@

~~D28&0.1 \footnotesize{(-0.5)}&0.0 \footnotesize{(-3.7)*}&0.0 \footnotesize{(-1.6)*}&0.1 \footnotesize{(\textbf{1.7})*}\tabularnewline
~~D4&0.1 \footnotesize{(\textbf{1.7})*}&0.0 \footnotesize{(\textbf{1.0})*}&0.0 \footnotesize{(-0.7)}&0.1 \footnotesize{(\textbf{2.0})*}\tabularnewline

@@

~~D7&0.1 \footnotesize{(\textbf{3.3})*}&0.0 \footnotesize{(\textbf{2.0})*}&0.1 \footnotesize{(-2.8)*}&0.1 \footnotesize{(\textbf{1.7})*}\tabularnewline
~~MD10&0.1 \footnotesize{(-1.8)*}&0.0 \footnotesize{(-6.5)*}&0.0 \footnotesize{(-3.3)*}&0.2 \footnotesize{(\textbf{0.4})}\tabularnewline
~~P8&0.2 \footnotesize{(\textbf{3.9})*}&0.1 \footnotesize{(\textbf{1.8})*}&0.2 \footnotesize{(\textbf{7.0})*}&0.6 \footnotesize{(\textbf{7.0})*}\tabularnewline

@@

~~C3&0.2 \footnotesize{(\textbf{0.7})*}&0.1 \footnotesize{(-1.0)*}&0.1 \footnotesize{(-0.3)}&0.2 \footnotesize{(\textbf{1.0})*}\tabularnewline

@@

~~D28&0.5 \footnotesize{(\textbf{0.7})*}&0.2 \footnotesize{(-0.1)}&0.3 \footnotesize{(\textbf{0.2})}&0.7 \footnotesize{(-1.0)*}\tabularnewline

@@

~~D6&0.4 \footnotesize{(-0.2)}&0.3 \footnotesize{(\textbf{4.1})*}&0.3 \footnotesize{(\textbf{1.4})*}&0.4 \footnotesize{(-1.0)*}\tabularnewline
~~D7&0.4 \footnotesize{(-1.0)*}&0.3 \footnotesize{(\textbf{3.4})*}&0.4 \footnotesize{(\textbf{0.4})}&0.4 \footnotesize{(-3.6)*}\tabularnewline

@@

~~P8&1.2 \footnotesize{(\textbf{2.0})*}&0.9 \footnotesize{(\textbf{2.3})*}&1.1 \footnotesize{(\textbf{2.0})*}&1.4 \footnotesize{(\textbf{1.0})*}\tabularnewline

@@

~~C10&1.1 \footnotesize{(-4.1)*}&1.3 \footnotesize{(-3.1)*}&1.6 \footnotesize{(-2.0)*}&1.7 \footnotesize{(-3.4)*}\tabularnewline

@@

~~D19&0.5 \footnotesize{(-2.8)*}&0.2 \footnotesize{(-1.0)*}&0.3 \footnotesize{(-1.6)*}&0.7 \footnotesize{(-2.3)*}\tabularnewline
~~D26&0.5 \footnotesize{(-1.9)*}&0.3 \footnotesize{(-1.7)*}&0.4 \footnotesize{(-1.0)*}&0.6 \footnotesize{(-0.8)*}\tabularnewline
~~D28&0.5 \footnotesize{(-3.0)*}&0.2 \footnotesize{(-4.9)*}&0.2 \footnotesize{(-4.9)*}&0.7 \footnotesize{(-2.1)*}\tabularnewline
~~D4&0.4 \footnotesize{(\textbf{0.0})}&0.4 \footnotesize{(-1.0)*}&0.4 \footnotesize{(-0.9)*}&0.5 \footnotesize{(\textbf{0.6})*}\tabularnewline
~~D6&0.5 \footnotesize{(-0.2)*}&0.5 \footnotesize{(-1.0)*}&0.5 \footnotesize{(-0.3)*}&0.5 \footnotesize{(-0.1)}\tabularnewline

@@

~~MD10&0.4 \footnotesize{(-2.3)*}&0.2 \footnotesize{(-3.7)*}&0.2 \footnotesize{(-4.4)*}&1.0 \footnotesize{(-1.8)*}\tabularnewline

@@

~~C10&0.0 \footnotesize{(-4.2)*}&0.0 \footnotesize{(-6.1)*}&0.0 \footnotesize{(-8.5)*}&0.1 \footnotesize{(-7.3)*}\tabularnewline
~~C3&0.3 \footnotesize{(\textbf{1.0})*}&0.3 \footnotesize{(-0.8)*}&0.4 \footnotesize{(-0.5)*}&0.2 \footnotesize{(-0.1)}\tabularnewline
~~D19&0.0 \footnotesize{(-1.9)*}&0.0 \footnotesize{(-0.4)}&0.0 \footnotesize{(-2.2)*}&0.1 \footnotesize{(-1.8)*}\tabularnewline

@@

~~D28&0.0 \footnotesize{(-1.7)*}&0.0 \footnotesize{(-0.2)}&0.0 \footnotesize{(-2.4)*}&0.1 \footnotesize{(-3.1)*}\tabularnewline
~~D4&0.1 \footnotesize{(\textbf{0.3})}&0.0 \footnotesize{(-1.3)*}&0.1 \footnotesize{(-0.3)}&0.1 \footnotesize{(\textbf{1.0})*}\tabularnewline
~~D6&0.1 \footnotesize{(-0.7)*}&0.1 \footnotesize{(-1.0)*}&0.1 \footnotesize{(\textbf{0.3})}&0.1 \footnotesize{(-0.3)*}\tabularnewline
~~D7&0.1 \footnotesize{(-2.2)*}&0.0 \footnotesize{(-2.1)*}&0.1 \footnotesize{(\textbf{1.3})*}&0.1 \footnotesize{(-0.4)*}\tabularnewline
~~MD10&0.0 \footnotesize{(-1.4)*}&0.0 \footnotesize{(-0.1)}&0.0 \footnotesize{(-0.8)*}&0.1 \footnotesize{(-4.3)*}\tabularnewline

@@

~~D19&0.4 \footnotesize{(-2.9)*}&0.2 \footnotesize{(-1.0)*}&0.3 \footnotesize{(-1.5)*}&0.6 \footnotesize{(-2.2)*}\tabularnewline

@@

~~D28&0.5 \footnotesize{(-3.0)*}&0.2 \footnotesize{(-5.4)*}&0.2 \footnotesize{(-5.2)*}&0.7 \footnotesize{(-1.7)*}\tabularnewline
~~D4&0.3 \footnotesize{(-0.1)}&0.3 \footnotesize{(-1.0)*}&0.3 \footnotesize{(-1.0)*}&0.4 \footnotesize{(\textbf{0.4})*}\tabularnewline
~~D6&0.4 \footnotesize{(-0.1)}&0.4 \footnotesize{(-1.0)*}&0.4 \footnotesize{(-0.4)*}&0.4 \footnotesize{(-0.1)}\tabularnewline

@@

~~MD10&0.4 \footnotesize{(-2.6)*}&0.1 \footnotesize{(-4.5)*}&0.2 \footnotesize{(-5.4)*}&1.0 \footnotesize{(-1.4)*}\tabularnewline
~~P8&1.3 \footnotesize{(-1.1)*}&1.1 \footnotesize{(-3.1)*}&1.6 \footnotesize{(-0.3)*}&2.2 \footnotesize{(\textbf{0.0})}\tabularnewline
